\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Juan Barbosa}

\section{Work experience}

\begin{eventlist}
\item{July 2016 -- Present}
     {Universidad de los Andes, Colombia}
     {JTA Computational Methods}
     
     \setlength{\leftskip}{0.5cm}
	     $\bullet$ \hspace{0.2cm} Introduced a set of Python algorithms to help the grading procedure, throw the systematic analysis of students code.
	     
	     $\bullet$ \hspace{0.2cm} Inspired students to develop computational sciences skills such as ODE, PCA, FFT.
     
	     $\bullet$ \hspace{0.2cm} Guided students to solve in class problems.
	     
	     \hrulefill
     \setlength{\leftskip}{0pt}   
	 
\item{January 2016 -- June 2016}
     {Universidad de los Andes, Colombia}
     {JTA Physics I}

	 \setlength{\leftskip}{0.5cm}
		 $\bullet$ \hspace{0.2cm} Developed course solutions to tests and exercises.
		 
		 \hrulefill
	 \setlength{\leftskip}{0pt} 

\item{July 2015 -- November 2015}
     {Universidad de los Andes, Colombia}
     {JTA Physics I}
     
	 \setlength{\leftskip}{0.5cm}
		 $\bullet$ \hspace{0.2cm} Developed course solutions to tests.
		 
		 $\bullet$ \hspace{0.2cm} Wrote performance reports of applied tests.
		 
		 \hrulefill
	 \setlength{\leftskip}{0pt}

\item{January 2015 -- June 2015}
     {Universidad de los Andes, Colombia}
     {JTA Astrobiology}
     
     \setlength{\leftskip}{0.5cm}     
	     $\bullet$ \hspace{0.2cm} Wrote performance reports of applied tests.
	     
	     $\bullet$ \hspace{0.2cm} Graded final projects.
     
	     \hrulefill
     \setlength{\leftskip}{0pt}
\end{eventlist}
\pagebreak
\personal
    [www.github.com/jsbarbosa]
    {Calle 126 \# 52 A 92 \newline Bogot\'a, Colombia}
    {57 (316) 7946510}
    {js.barbosa10@uniandes.edu.co}

\section{Education}

\begin{yearlist}

\item{2014 -- Present}
     {Chemistry major}
     {Universidad de los Andes, Colombia}
     
\item{2013 -- Present}
     {Physics major}
     {Universidad de los Andes, Colombia}
     
\item[Diploma]{2013}
     {Astronomy seminar}
     {Universidad Sergio Arboleda, Colombia}

\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{2016}
     {SpecPy (\href{http://github.com/jsbarbosa/specpy}{github.com/jsbarbosa/specpy})}
     {Real time Spectrum Analyzer}

\item{2016}
     {BlinkDetection (\href{http://tip.entidi.com/}{github.com/jsbarbosa/Blink-Detection})}
     {Detect blinking using a web camara}

\item{2015}
     {Rutherford Chemistry}
     {Gas chromatography - mass spectrometry software}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Spanish}{Native speaker}
\item{English}{Oral: fair -- Written: fair}
\item{French}{Oral: proficient -- Written: bad}

\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {Python, Java, Shell, Linux, \LaTeX}

\item{Intermediate}
     {C, git, PHP, HTML}

\item{Basic level}
     {Mathematica, VBA}

\end{factlist}

\end{document}
